---
title: "My R Markdown Prime"
output: html_document
date: "2025-11-16"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

R Markdown is a tool that lets you combine text, R code, and math in one document. When you knit the file, R Markdown runs the code and creates a clean, reproducible report. This makes it easier to keep your analysis organized and up to date, and it ensures that your results always match the code you’ve written. I also like that you can include LaTeX math expressions, which makes presenting formulas and calculations much clearer.

# Narrtive
One thing I like about R Markdown is that I can write my explanation and show my code in the same place. If I ever change the dataset or update the code, the results and plots automatically refresh when I knit the file. This helps keep everything consistent without needing to copy and paste results into a separate document. I also appreciate how it integrates text, visuals, and code seamlessly, making my reports more professional and easier to follow.

## LaTeX Math Examples
Inline example: $ \alpha + \beta = \gamma $

Displayed equation:

\[
E = mc^2
\]


```{r cars}
library(ggplot2)
data("mtcars")
head(mtcars)

```

## Including Plots

You can also embed plots, for example:

```{r Analysis and Plot}

summary(mtcars$mpg)

ggplot(mtcars, aes(x = wt, y = mpg)) +
geom_point() +
geom_smooth(method = "lm") +
labs(title = "MPG vs Weight",
x = "Weight (1000 lbs)",
y = "Miles per Gallon")

```

# Reflection

Using R Markdown felt really different from writing a regular report, but in a good way. I liked having my text, code, math, and graphs all in the same place instead of switching between programs. It also saved time because everything updates automatically when the code runs. When I compared my .Rmd file to the knitted HTML, I was surprised by how clean and polished the final document looked. The biggest surprise was how simple it was to add things like math formulas and plots with just a few lines of code. Overall, R Markdown made the whole reporting process easier, cleaner, and more organized.